The Astropy Project

### 2017-11-20 main.tex
fits section

\subsubsection{FITS}
% \subsubsection{\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})}

The \package{astropy.io.fits} subpackage now provides command-line
scripts for printing a summary of the HDUs in a FITS file(s)
(\texttt{fitsinfo}) and for printing the header information
to the screen in a human-readable format (\texttt{fitsheader}).

% \subsubsection{\texttt{.fits}: lazy loading }

The \package{astropy.io.fits} subpackage now supports \emph{lazy
loading}, where all HDUs are not loaded until they are requested (or
the file is closed). This should provide substantial speedups for
situations using the convenience functions (e.g., \texttt{getheader()}
or \texttt{getdata()}) to get HDU’s that are near the front of a file
with many HDUs.

>>>>

\subsubsection{FITS}

The \package{astropy.io.fits} subpackage started as a direct port of the
PyFITS project. Therefore it is pretty stable, with mostly bug fixes but also
a few new features and performance improvements.  The API remains compatible
with PyFITS, which is now deprecated in favor of Astropy.

Command-line scripts are now available for printing a summary of the HDUs in
a FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
the screen in a human-readable format (\texttt{fitsheader}).

FITS files are now loaded \emph{lazily} (the default behavior, which can be
deactivated if needed), where all HDUs are not loaded until they are requested
(or the file is closed). This should provide substantial speedups for
situations using the convenience functions (e.g., \texttt{getheader()} or
\texttt{getdata()}) to get HDU’s that are near the front of a file with many
HDUs.
